---
title: "Vulnerable marine ecosystem assessment <img src=\"C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/iceslogo.png\" style=\"float: right;\"/>"
author: "ICES"
date: "April 2022"
output: html_document
chunk_output_type: console
#runtime: shiny
editor_options: 
  chunk_output_type: console
---
<style>
.html-widget {
    margin: auto;

}
</style>


<style type="text/css">
  body{
  font-size: 11pt;
  font-family: times, serif;
  text-align: justify;
  }
  table,td,th {
    font-size: 10pt;
    font-family: times, serif;
  }
  a {
    color: #6FA388;
    text-decoration: none;
    font-weight: bold;
  }
  .nav-pills>li.active>a, .nav-pills>li.active>a:focus, .nav-pills>li.active>a:hover {
    color: #fff;
    background-color: #6FA388;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = "allow")
pathdir <- "C:/Users/danie/Documents/Online for git/VME-Advice"
pathdir_nogit <- "C:/Users/danie/Documents/Online for git/VME-advice_noGIT" # stores the VMS and VME data from sharepoint
icespal <- c('#939DBD','#012B5B','#7FA99C')
names(icespal)<- c('lb','db','lg')
  
source(paste(pathdir,"Utilities/Libraries_VMEadvice.R",sep="/"))  
  
# Load source data for map layer key tables
  map1layers <- openxlsx::read.xlsx(paste(pathdir,"Output/MapLayerDesc.xlsx",sep="/"),1)
  map2layers <- openxlsx::read.xlsx(paste(pathdir,"Output/MapLayerDesc.xlsx",sep="/"),2)
  scenop     <- openxlsx::read.xlsx(paste(pathdir,"Output/ScenarioOptions.xlsx",sep="/"),1)
# Load source data used for tables 1 and 2
  load(paste(pathdir,"2-Data processing/Table1_underlyingdata.RData",sep="/"))
# set data call year
  datacallyear <- 2021
  newyear_fished <- (datacallyear-1):(datacallyear-3)
```


**Available evidence on the occurrence of Vulnerable marine ecosystems (VMEs), fishing activity in relation to VMEs, and spatial management options to minimise the risk from fishing activities to VMEs**

#  {.tabset .tabset-fade .tabset-pills}

## Celtic Seas {.tabset}
```{r CS,include=FALSE}
  Region_ID <- "Celtic Seas"
  Region_ID_Excel <- "Celtic Seas"
  # define fishable domain - either EU or NEAFC 
  FishD <- "EU"
```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_ICES_Regions.Rmd'}
```

## Bay of Biscay and the Iberian Coast {.tabset}
```{r BoBIC,include=FALSE}
  Region_ID <- "Bay of Biscay and the Iberian Coast"
  Region_ID_Excel <- "BoBIC"
  # define fishable domain - either EU or NEAFC 
  FishD <- "EU"
```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_ICES_Regions.Rmd'}
```

## Greater North Sea {.tabset}
```{r GNS,include=FALSE}
  Region_ID <- "Greater North Sea"
  Region_ID_Excel <- "Greater North Sea"
  # define fishable domain - either EU or NEAFC 
  FishD <- "EU"
```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_ICES_Regions.Rmd'}
```

## Azores {.tabset}
```{r Az,include=FALSE}
  Region_ID <- "Azores"
  Region_ID_Excel <- "Azores"
  # define fishable domain - either EU or NEAFC 
  FishD <- "EU"
```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_ICES_Regions.Rmd'}
```

## Icelandic Waters {.tabset}
```{r IW,include=FALSE}
  Region_ID <- "Icelandic Waters"
  Region_ID_Excel <- "Icelandic Waters"
  # define fishable domain - either EU or NEAFC 
  FishD <- "EU"
```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_ICES_Regions.Rmd'}
```

# {-}