---
title: "EU vulnerable marine ecosystem assessment <img src=\"C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/iceslogo.png\" style=\"float: right;\"/>"
author: "ICES"
date: "April 2022"
output: html_document
chunk_output_type: console
#runtime: shiny
editor_options: 
  chunk_output_type: console
---
<style>
.html-widget {
    margin: auto;

}
</style>


<style type="text/css">
  body{
  font-size: 11pt;
  font-family: times, serif;
  text-align: justify;
  }
  table,td,th {
    font-size: 10pt;
    font-family: times, serif;
  }
  a {
    color: #6FA388;
    text-decoration: none;
    font-weight: bold;
  }
  .nav-pills>li.active>a, .nav-pills>li.active>a:focus, .nav-pills>li.active>a:hover {
    color: #fff;
    background-color: #6FA388;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = "allow")

  pathdir       <- "C:/Users/danie/Documents/Online for git/VME-Advice"
  pathdir_nogit <- "C:/Users/danie/Documents/Online for git/VME-advice_noGIT" # stores the VMS and VME data from sharepoint
  icespal       <- c('#939DBD','#012B5B','#7FA99C')
  names(icespal)<- c('lb','db','lg')
    
  source(paste(pathdir,"Utilities/Libraries_VMEadvice.R",sep="/"))  

  # load all data layers for rmarkdown (including the datacall year)
  load(paste(pathdir,"2-Data processing/Map_layers_workspace.RData",sep="/")) 
  
  # set the most recent fishing years
  newyear_fished <- (datacallyear_VMS-1):(datacallyear_VMS-3)

# Load source data for map layer key tables
  map1layers <- openxlsx::read.xlsx(paste(pathdir,"Output/MapLayerDesc.xlsx",sep="/"),1)
  map2layers <- openxlsx::read.xlsx(paste(pathdir,"Output/MapLayerDesc.xlsx",sep="/"),2)
  scenop     <- openxlsx::read.xlsx(paste(pathdir,"Output/ScenarioOptions.xlsx",sep="/"),1)

  # Load source data used for table 1
  load(paste(pathdir,"2-Data processing/Table1_underlyingdata.RData",sep="/"))

```


**Available evidence on the occurrence of Vulnerable marine ecosystems (VMEs), fishing activity in relation to VMEs, and spatial management options to minimise the risk from fishing activities to VMEs**

# Assessment Overview {.tabset .tabset-fade .tabset-pills}

## Assessment Area
```{r, include=FALSE}
eu_mxt <- #st_bbox(eu_map)
  nam <- c("EU regions with VME")
# 
  eu_mfs <- leaflet() %>%
    fitBounds(eu_mxt[[1]],eu_mxt[[2]],eu_mxt[[3]],eu_mxt[[4]]) %>%
    addProviderTiles(providers$Esri.WorldImagery)%>%
   # boundaries
    addPolygons(data = eu_map, group = nam[1],
                stroke = TRUE, fillOpacity = 0, smoothFactor = 0.5, opacity = 0.5, weight = 1, color = "white")
```

**Areas include in the current vulnerable marine ecosystem assessment**
```{r echo=FALSE, message=FALSE,fig.asp=0.8,out.width='85%', fig.cap="** **"}
eu_mfs
```

## Advice Summary

To be completed following input from regional experts
## Assessment background

[Link to  request](https://www.ices.dk/Pages/default.aspx)

## Assessment methodology

[Links to  relevent  WG documentation](https://www.ices.dk/Pages/default.aspx)
## Sources and References

ADG to provide 
## {-}

#  {.tabset .tabset-fade .tabset-pills}

```{r EU,include=FALSE}
  Region_ID <- c("France","Ireland","Azores","Spain","Portugal","Denmark",
                 "Netherlands","Germany","Sweden","Belgium")
  Region_ID_Excel <- "EUVME"

```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_EUwaters.Rmd'}
```

# {-}