---
title: "Vulnerable marine ecosystem assessment <img src=\"C:/Users/neilm/Documents/projects/VME-Advice/Utilities/iceslogo.png\" style=\"float: right;\"/>"
author: "ICES"
date: "September 2022"
output: html_document
chunk_output_type: console
#runtime: shiny
editor_options: 
  chunk_output_type: inline
---
---
<style>
.html-widget {
    margin: auto;

}
</style>


<style type="text/css">
  body{
  font-size: 11pt;
  font-family: times, serif;
  text-align: justify;
  }
  table,td,th {
    font-size: 10pt;
    font-family: times, serif;
  }
  a {
    color: #6FA388;
    text-decoration: none;
    font-weight: bold;
  }
  .nav-pills>li.active>a, .nav-pills>li.active>a:focus, .nav-pills>li.active>a:hover {
    color: #fff;
    background-color: #6FA388;
}
</style>

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE)
  knitr::opts_chunk$set(warning = FALSE)
  knitr::opts_chunk$set(message = FALSE)
  options(knitr.duplicate.label = "allow")
  
  pathdir       <- "C:/Users/neilm/Documents/projects/VME-Advice"
  pathdir_nogit <- "C:/Users/neilm/Documents/VME-advice_noGIT" # stores the VMS and VME data from sharepoint
  icespal       <- c('#939DBD','#012B5B','#7FA99C')
  names(icespal)<- c('lb','db','lg')
  datacallyear_VMS <- 2021
  fishing_data <- "NEAFC"
    
  source(paste(pathdir,"Utilities/Libraries_VMEadvice.R",sep="/"))  

  # load all data layers for rmarkdown (including the datacall year)
  load(paste(pathdir,"2-Data processing", paste(datacallyear_VMS, fishing_data, "Map_layers_workspace.RData", sep = "_"), sep="/")) 
  
  # set the most recent fishing years
  newyear_fished <- (datacallyear_VMS-1):(datacallyear_VMS-3)
    
# Load source data for map layer key tables
  map1layers <- openxlsx::read.xlsx(paste(pathdir,"Output/MapLayerDesc.xlsx",sep="/"),1)
  map2layers <- openxlsx::read.xlsx(paste(pathdir,"Output/MapLayerDesc.xlsx",sep="/"),2)
  scenop     <- openxlsx::read.xlsx(paste(pathdir,"Output/ScenarioOptions.xlsx",sep="/"),1)

  # Load source data used for table 1
  load(paste(pathdir,"2-Data processing/Table1_underlyingdata.RData",sep="/"))
  

```


**Available evidence on the occurrence of Vulnerable marine ecosystems (VMEs), fishing activity in relation to VMEs, and spatial management options to minimise the risk from fishing activities to VMEs**

#  {.tabset .tabset-fade .tabset-pills}

## Overview Tab {.tabset}
```{r overview, include=FALSE}
#
```
## Region 1 {.tabset}
```{r NEAFC1,include=FALSE}
  Region_ID <- "Region_1"
  Region_ID_Excel <- "Region 1"
  # define fishable domain - either EU or NEAFC 
  FishD <- "NEAFC"
```

## Region 2 {.tabset}
```{r NEAFC2,include=FALSE}
  Region_ID <- "Region_2"
  Region_ID_Excel <- "Region 2"
  # define fishable domain - either EU or NEAFC 
  FishD <- "NEAFC"
```

## Region 3 {.tabset}
```{r NEAFC3,include=FALSE}
  Region_ID <- "Region_3"
  Region_ID_Excel <- "Region 3"
  # define fishable domain - either EU or NEAFC 
  FishD <- "NEAFC"
```

```{r add-to-main, child = 'C:/Users/neilm/Documents/projects/VME-Advice/Utilities/rmarkdown_NEAFC_Regions.Rmd'}
```

# {-}
