---
title: "Vulnerable marine ecosystem assessment"
author: "ICES"
date: "April 2022"
output: html_document


chunk_output_type: console
#runtime: shiny

---
<style>
.html-widget {
    margin: auto;

}
</style>


<style type="text/css">
  body{
  font-size: 11pt;
  font-family: times, serif;
  text-align: justify;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pathdir <- "C:/Users/danie/Documents/Online for git/VME-advice"
pathdir_nogit <- "C:/Users/danie/Documents/Online for git/VME-advice_noGIT" # stores the VMS and VME data from sharepoint
  
source(paste(pathdir,"Utilities/Libraries_VMEadvice.R",sep="/"))  
  
# load the workspace with all layers
load(paste(pathdir,"2-Data processing/Map_layer_workspace.RData",sep="/"))  

# set the ecoregion of interest
  subreg <- subset(ICESEcReg,ICESEcReg$Ecoregion =="Celtic Seas")
  scen11 <- st_intersection(scen11,subreg)
  scen12 <- st_intersection(scen12,subreg)
  scen21 <- st_intersection(scen21,subreg)
  scen22 <- st_intersection(scen22,subreg)
  shapeEEZ <- st_intersection(shapeEEZ,subreg)
  EUFootp <- st_intersection(EUFootp,subreg)
  EUFootp_mob <- st_intersection(EUFootp_mob,subreg)
  EUFootp_stat <- st_intersection(EUFootp_stat,subreg)
  Footprint_both <- st_intersection(Footprint_both,subreg)
  Footprint_mobile <- st_intersection(Footprint_mobile,subreg)
  Footprint_static <- st_intersection(Footprint_static,subreg)
  NEAFCFootp <- st_intersection(NEAFCFootp,subreg)
  NEAFCReg <- st_intersection(NEAFCReg,subreg)
  clos_EU <- st_make_valid(clos_EU)
  clos_EU <- st_intersection(clos_EU,subreg)
  clos_neafc <- st_intersection(clos_neafc,subreg)
  VMEgrid_new <- st_intersection(VMEgrid_new,subreg)
  VMEgrid_old <- st_intersection(VMEgrid_old,subreg)
  Elements <- st_intersection(Elements,subreg)
  Reg_depth <- st_intersection(Reg_depth,subreg)

```
**Available evidence on the occurrence of Vulnerable marine ecosystems (VMEs), fishing activity in relation to VMEs, and spatial management options to minimise the risk from fishing activities to VMEs**

#  {.tabset .tabset-fade .tabset-pills}

## Celtic Seas {.tabset}
```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_CelticS.Rmd'}
```

## Bay of Biscay and the Iberian Coast {.tabset}

## NEAFC Reykjanes Ridge {.tabset}

# {-}