---
title: "Vulnerable marine ecosystem assessment <img src=\"C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/iceslogo.png\" style=\"float: right;\"/>"
author: "ICES"
date: "April 2022"
output: html_document
chunk_output_type: console
#runtime: shiny
editor_options: 
  chunk_output_type: console
---
<style>
.html-widget {
    margin: auto;

}
</style>


<style type="text/css">
  body{
  font-size: 11pt;
  font-family: times, serif;
  text-align: justify;
  }
  table,td,th {
    font-size: 10pt;
    font-family: times, serif;
  }
  a {
    color: #6FA388;
    text-decoration: none;
    font-weight: bold;
  }
  .nav-pills>li.active>a, .nav-pills>li.active>a:focus, .nav-pills>li.active>a:hover {
    color: #fff;
    background-color: #6FA388;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

pathdir <- "C:/Users/danie/Documents/Online for git/VME-Advice"
pathdir_nogit <- "C:/Users/danie/Documents/Online for git/VME-advice_noGIT" # stores the VMS and VME data from sharepoint

icespal <- c('#939DBD','#012B5B','#7FA99C')
names(icespal)<- c('lb','db','lg')
  
source(paste(pathdir,"Utilities/Libraries_VMEadvice.R",sep="/"))  
  
# load the workspace with all layers
  load(paste(pathdir,"2-Data processing/Map_layer_workspace.RData",sep="/"))  

# Load source data for map layer key tables
  map1layers <- openxlsx::read.xlsx('C:/Users/danie/Documents/Online for git/VME-Advice/Output/MapLayerDesc.xlsx',1)
  map2layers <- openxlsx::read.xlsx('C:/Users/danie/Documents/Online for git/VME-Advice/Output/MapLayerDesc.xlsx',2)
#  scenop     <- openxlsx::read.xlsx('C:/Users/danie/Documents/Online for #git/VME-Advice/Output/ScenarioOptions.xlsx',1)
  
  
# Load source data used for tables 1 and 2
  load(paste(pathdir,"2-Data processing/Table1_underlyingdata.RData",sep="/"))

# define fishable domain in table 2 - for now either EU or NEAFC 
  FishD <- "EU"

# set data call year
  datacallyear <- 2021
  newyear_fished <- (datacallyear-1):(datacallyear-3)

```



**Available evidence on the occurrence of Vulnerable marine ecosystems (VMEs), fishing activity in relation to VMEs, and spatial management options to minimise the risk from fishing activities to VMEs**

#  {.tabset .tabset-fade .tabset-pills}

## Celtic Seas {.tabset}

```{r region subset,include=FALSE}

  Region_ID <- "Celtic Seas"

# set the ecoregion of interest
  subreg <- subset(ICESEcReg,ICESEcReg$Ecoregion ==Region_ID)
  scen11 <- st_intersection(st_make_valid(scen11),subreg)
  scen12 <- st_intersection(scen12,subreg)
  scen21 <- st_intersection(scen21,subreg)
  scen22 <- st_intersection(scen22,subreg)
  shapeEEZ <- st_intersection(shapeEEZ,subreg)
  EUFootp <- st_intersection(EUFootp,subreg)
  #EUFootp_mob <- st_intersection(EUFootp_mob,subreg)
 # EUFootp_stat <- st_intersection(EUFootp_stat,subreg)
  #Footprint_both <- st_intersection(Footprint_both,subreg)
  #Footprint_mobile <- st_intersection(Footprint_mobile,subreg)
  #Footprint_static <- st_intersection(Footprint_static,subreg)
  NEAFCFootp <- st_intersection(NEAFCFootp,subreg)
  NEAFCReg <- st_intersection(NEAFCReg,subreg)
  #clos_EU <- st_make_valid(clos_EU)
  #clos_EU <- st_intersection(clos_EU,subreg)
  clos_neafc <- st_intersection(clos_neafc,subreg)
  VMEgrid_new <- st_intersection(VMEgrid_new,subreg)
  VMEgrid_old <- st_intersection(VMEgrid_old,subreg)
  Elements <- st_intersection(Elements,subreg)
  Reg_depth <- st_intersection(Reg_depth,subreg)

```

```{r add-to-main, child = 'C:/Users/danie/Documents/Online for git/VME-Advice/Utilities/rmarkdown_ICES_Regions.Rmd'}
```

## Bay of Biscay and the Iberian Coast {.tabset}

## NEAFC Reykjanes Ridge {.tabset}

# {-}